Translation of B Implementations to the LLVM: Specification

### 2014-03-17 DOCUMENTATION/specification.tex
Added spec rules for initialization (still incomplete).

Initialization is done is two steps: first all imported modules are
initialized,  second the initialization clause is executed.
\begin{align*}
  \trad{i}{Init} \isdef
  & \llvm{"define void @\PH{\B{i.id}}\$init\$() \{ \nl"} \\
  & \quad\llvm{\PH{\trad{i, i.impl}{\ListOf{InitImp}}}} \\
  & \quad\llvm{\PH{\trad{i.init, "exit"}{\ListOf{\B{Inst}}}_L}} \\
  & \quad\llvm{exit: ret void \nl} \\
  & \llvm{\}"}
\end{align*}
The initialization of an imported module is performed by a call to the
corresponding initialization function:
\begin{align*}
  \lefteqn{\trad{\B{impl}, \B{impo}}{InitImp} \isdef} \\
  & \LET v = \variable \AND \B{m} = \B{impo.mach} \IN \\
  & \quad \llvm{"\PH{v} = getelementptr \PH{\state(\B{impl.root})}* \%self\$, i32 0, i32 \PH{\idx(\B{impo})}\nl}\\
  & \quad \llvm{call void @\PH{\B{m.id}}\$init\$(\PH{\state(\B{m.impl})}*
    \PH{\ell}) \nl"}
\end{align*}

>>>>

Initialization of a module is implemented by a LLVM function that takes as
parameters: the address of the aggregate representing the state of the module,
which we name \llvm{\%self}, and the addressses of the aggregates representing
the state of each component of the module, which we name \llvm{\%argN}, where
\llvm{N} is a numeric identifier. The body of this function is composed as
follows: first frame stack memory is allocated, to store the representation of
the local variables in the initialization; second, all imported modules are
bound to the component's elements and initialized; last the instructions
composing the initialization clause are executed:

\begin{align*}
  \trad{\B{n}}{\B{init}}_{\text{interface}} \isdef
  & \llvm{"define void \PH{\init(\B{n})} ( \PH{\stateref(\B{n})} \%self,
    \PH{\trad{\trimportedinstances(\B{n})}{\B{args}}} \{ \nl"} \\
  & \quad\llvm{entry: \nl} \\
  & \quad\llvm{\PH{\trad{i.init}{alloc}}} \\
  & \quad\llvm{\PH{\trad{i, i.impl}{\ListOf{InitImp}}}} \\
  & \quad\llvm{\PH{\trad{i.init, "exit"}{\ListOf{\B{Inst}}}_L}} \\
  & \quad\llvm{exit: ret void \nl} \\
  & \llvm{\}"}
\end{align*}

Next, we specify how to generate the code to enumerate the list of arguments
representing the components. Essentially, for each stateful component
\B{inst}, the argument is a reference to the aggregate representing the
state and named \llvm{\%argN}, where \llvm{N} is a number:
\begin{align*}
  \trad{}{args} \isdef & \llvm{""} \\
  \trad{\B{inst} L}{args} \isdef &
  \llvm{"\trad{\B{inst}, \textit{index}(\B{inst}, L)}{arg}, \trad{L}{args}"} \\
  \trad{\B{inst}, $n$}{arg} \isdef &
  \llvm{""} \triangleleft \stateless(\B{inst.mach}) \triangleright 
  \llvm{"\PH{\stateref(\B{inst.mach})} \%arg\PH{n}"}
\end{align*}

The initialization of an imported module is performed by a call to the
corresponding initialization function:
\begin{align*}
  \lefteqn{\trad{\B{impl}, \B{impo}}{InitImp} \isdef} \\
  & \LET v = \variable \AND \B{m} = \B{impo.mach} \IN \\
  & \quad \llvm{"\PH{v} = getelementptr \PH{\state(\B{impl.root})}* \%self\$, i32 0, i32 \PH{\idx(\B{impo})}\nl}\\
  & \quad \llvm{"store \PH{?ref} \%arg\PH{?X}, \PH{?ref} * \PH{\idx(\B{impo})}\nl}\\
  & \quad \llvm{call void @\PH{\B{m.id}}\$init\$(\PH{\state(\B{m.impl})}*
    \PH{\ell}) \nl"}
\end{align*}
+ add binding!
